High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-07-23 inst/manuscript/si.tex
Added dataset documentation, manuscript statement (EarthArxiv), several datasets

\hypertarget{assessing-quality-of-composites}{%
\subsection{Assessing quality of
composites}\label{assessing-quality-of-composites}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  After determining the class, if
\end{enumerate}

@@

@@

\hypertarget{active-learning-process}{%
\subsection{Active learning process}\label{active-learning-process}}

@@

The locations of training, training reference, and validation points are
shown in Figure \ref{fig:trainval}. In AOI 3, the initial active
learning cycle resulted in low accuracy because the northern part of the
AOI shows low contrast between fields and the surrounding vegetation in
the dry season. Training the model with the initial 500 samples resulted
in large commission errors in this part of the AOI, thus we ran a second
active learning cycle that began with an inital random draw of 300
training sites confined to this AOI (blue points in Figure
\ref{fig:trainval}A)

@@

The distribution of data collection effort and scores from training
reference sites by labelling team are shown in Figure
\ref{fig:trainqual}. These results include those from re-labelling the
initial training in Cluster 2 (AOIs 7-9, 12, 15). This was done because
we discovered a small spatial offset in the original image composites,
which we corrected by reprocessing the images. We replaced the image
overlays in the instance for central-southeast (Figure
\ref{fig:trainval}A), and the labelling team mapped these sites a second
time during the production run in late 2019. The reprocessed labels were
used to initially train the model for AOIs 9, 12, and 15.

@@

{\centering \includegraphics[width=0.5\linewidth,]{figures/si_training_qual_n}

@@

\caption{The A) distributions of scores at training reference sites for each labeller (means indicated by X in boxplots), and B) the number of training and training reference sites completed by each labeller. Labellers' identities are anonymized.}\label{fig:trainqual}
\end{figure}

The average Bayesian Risk of each training and validation site is shown
in Figure \ref{fig:labelrisk}, as well as the distribution of risk
values per AOI and the initial training clusters (Figure
\ref{fig:labelriskhist}). The three initial clusters include the second
mapping of Cluster 2.

@@

\hypertarget{validation}{%
\subsubsection{Validation}\label{validation}}

The differences in accuracy, AUC, and F1 between the active learning
process and the random retraining at each iteration for AOIs 1, 8, and
15 (Figure \ref{fig:randomvactive}). Small differences due to random
variations in the RandomForest models are the reason for the non-zero
differences at iteration 0, when both models were trained with the same
level set.\\

Probability images resulting from Random Forests models trained with
labels generated under three different labeling strategies are
illustrated in Figure \ref{fig:labelstrategy}. These included consensus
labels, and those individual labels that were likely to be the most and
least accurate for each training site. Label accuracy was based on the
mean score of each labeller against the training reference sites (Figure
\ref{fig:trainqual}), as assessed when labelling a given AOI. These
images were created for a single tile in AOI 1.

@@

\hypertarget{reference-label-uncertainty}{%
\subsubsection{Reference label
uncertainty}\label{reference-label-uncertainty}}

>>>>

\hypertarget{map-reference-system}{%
\subsection{Map reference system}\label{map-reference-system}}

The map reference system used in our mapping approach had three
different levels. At the coarsest level, Ghana was divided into 16
different mapping zones, or areas of interest (AOIS; Figure
\ref{fig:aois}A), that were used to create AOI-specific mapping models.
Each AOIs was comprised of 400 to 777 adjacent tiles. These tiles were
used to create seasonal image composites, and were defined within a 0.05
degree grid (Figure \ref{fig:aois}B)), with each tile numbered to
correspond to a larger 1 degree grid cell that it sits within (dotted
lines in Figure \ref{fig:aois}B). Training and reference labels were
created within a 0.005 degree grid that nested within each tile (Figure
\ref{fig:aois}C). Therefore, each tile has 100 grid cells, and there are
400 tiles per 1X1 degree. The smallest AOI consists of a single 1X1
degree, which fall in the center of the country (AOIs 5, 8, 11, and 14).
AOIs falling along Ghana's boundaries were created by tiles from 1X1
degree cells that straddled Ghana's border with those from the closest
degree cells that were fully contained within Ghana (e.g.~AOI 1), with
the exception of AOI 16, which was comprised of tiles in three partial
1X1 degree cells along Ghana's coast.

{\centering \includegraphics[width=1\linewidth,]{figures/reference_system}

\caption{The reference system used in this mapping approach, including A) numbered areas of interest (AOIs) that define the minimum mapping geography (solid black lines; dotted lines indicate boundaries of 1 degree grid), B) the 0.05 degree tile used for compositing imagery, and C) the 0.005 degree resolution reference grid used for collecting training data and distributed computing.}\label{fig:aois}
\end{figure}

\hypertarget{image-compositing}{%
\subsection{Image compositing}\label{image-compositing}}

\hypertarget{variation-in-lengths-of-temporal-window-used}{%
\subsubsection{Variation in lengths of temporal window
used}\label{variation-in-lengths-of-temporal-window-used}}

The typical window for compositing dry season imagery was December, 2018
to February, 2019, but in the cloudiest regions (AOIs 10, 11, 13, 14,
16) we started the dry season window in November, to ensure a sufficient
density of images for compositing.

\hypertarget{assessing-composite-quality}{%
\subsubsection{Assessing composite
quality}\label{assessing-composite-quality}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  After determining the class, if:
\end{enumerate}

@@

\hypertarget{map-reference-label-uncertainty}{%
\paragraph{Map reference label
uncertainty}\label{map-reference-label-uncertainty}}

\hypertarget{accuracy-assessment-zones}{%
\paragraph{Accuracy assessment zones}\label{accuracy-assessment-zones}}

The zones used to assess regional variation in map accuracy are
illustrated in Figure \ref{fig:aoizones}.

@@

\hypertarget{mapping-cropland-probabilities-with-active-learning}{%
\subsection{Mapping cropland probabilities with active
learning}\label{mapping-cropland-probabilities-with-active-learning}}

The number of active learning iterations per AOI was three, for all but
four AOIs. AOIs 10 and 14 stopped after one and two iterations,
respectively, as they started with high initial validation accuracies
(\textgreater83\%) and showed little subsequent improvement. The models
for these two AOIs were thus trained with 600 - 700 labels. AOI 15 was
run for 4 iterations (900 samples), while AOI 3 underwent a second
active learning cycle because the model produced during the first cycle
was inaccurate (see next section). In this second run, 300 initial
training sites randomly selected within the AOI were used, followed by 2
subsequent active learning iterations, resulting in a training sample of
500.

@@

The locations of training, training reference, and validation points are
shown in Figure \ref{fig:trainval}. In AOI 3, the initial active
learning cycle resulted in low accuracy because the northern part of the
AOI shows low contrast between fields and the surrounding vegetation in
the dry season. Training the model with the initial 500 samples resulted
in large commission errors in this part of the AOI, thus we ran a second
active learning cycle that began with an inital random draw of 300
training sites confined to this AOI (blue points in Figure
\ref{fig:trainval}A).

@@

The distribution of training and validation sample collection effort was
divided across 20 labellers, with a core group of 13 who completed more
than 1,000 assignment each (Figure \ref{fig:assignmentcount}). As each
training/validation task was undertaken by 4 separate labellers, 34,014
sets of labels were made. Each labeller digitized an average of 2,001
training/validation assignments.

@@

{\centering \includegraphics[width=0.8\linewidth,]{figures/si_training_n}

@@

\caption{The A) number of training/validation and accuracy assessment assignments completed by each labeller, and B) the distributions of quality scores at training reference sites for each labeller (means indicated by X in boxplots). Labellers' identities are anonymized.}\label{fig:assignmentcount}
\end{figure}

These results include those from re-labelling the initial training in
Cluster 2 (AOIs 7-9, 12, 15). This was done because we discovered a
small spatial offset in the original image composites, which we
corrected by reprocessing the images. We replaced the image overlays in
the instances for this Cluster (Figure \ref{fig:trainval}A), and the
labelling team mapped these sites a second time during the production
run in late 2019. The reprocessed labels were used to initially train
the model for AOIs 9, 12, and 15.

\hypertarget{model-performance}{%
\subsubsection{Model performance}\label{model-performance}}

The differences in accuracy, AUC, and F1 between the active learning
process and the random retraining at each iteration for AOIs 1, 8, and
15 (Figure \ref{fig:randomvactive}). Small differences due to random
variations in the RandomForest models are the reason for the non-zero
differences at iteration 0, when both models were trained with the same
level set.

The lower accuracy of actively versus randomly trained models in earlier
iterations was caused by results at AOI 15, where active learning
accuracy was 8.37 percent lower than random training after iteration 1
(see Figure \ref{fig:randomvactive}). In comparison, iteration 1 active
learning accuracies were 2.88 and 0.45 percent higher than random
training for AOIs 1 and 8, respectively. Accuracy under active learning
for AOI 15 exceeded randomized training after 4 iterations.

Two measures of label quality, average quality score per labeller and
the Bayesian Risk of labels, were calculated to provide proxy measures
of label error. Labeller quality was scored 9,389 times against 98
unique training reference sites, with each labeller assessed an average
of 552 times at a rate of 1 training reference site for every 3.62
training site mapped. The mean of each labeller's average accuracy score
was 0.71 (range 0.6 to 0.85; Figure \ref{fig:labelqual}).

{\centering \includegraphics[width=0.7\linewidth,]{figures/si_label_quality}

\caption{Boxplots showing the distributions of quality scores from the accuracy assessment assignments undertaken by each labeller (means indicated by X in boxplots). Labellers' identities are anonymized.}\label{fig:labelqual}
\end{figure}

The average Bayesian Risk of each training and validation site is shown
in Figure \ref{fig:labelrisk}, as well as the distribution of risk
values per AOI and the initial training clusters (Figure
\ref{fig:labelriskhist}). The three initial clusters include the second
mapping of Cluster 2 (Figure \ref{fig:trainval}A).

@@

The average Bayesian risk was 0.122 for training labels and 0.127 for
validation labels. Risk was highest in the northern AOIs (AOIs 1-6;
Figures S6-7), falling between 0.157 for training and 0.173 for
validation labels (Figures S6-7), and lowest in the southwestern AOIs
(AOIs 10, 11, 13, 14, 16; training risk = 0.079; validation risk =
0.065). Label risk in the central-southeastern AOIs (AOIs 7-9, 12, 15)
was slightly lower (training = 0.127; validation = 0.136) than in the
north. Labeller experience also appeared to reduce risk, which we
observed during a relabelling of the 500 initial random site in this
cluster; the mean risk of the updated labels was 0.055, compared to
0.172 for original labels.

Probability images resulting from Random Forests models trained with
labels generated under three different labeling strategies are
illustrated in Figure \ref{fig:labelstrategy}. These included consensus
labels, and those individual labels that were likely to be the most and
least accurate for each training site. Label accuracy was based on the
mean score of each labeller against the training reference sites (Figure
\ref{fig:labelqual}), as assessed when labelling a given AOI. These
images were created for a single tile in AOI 1.

@@
